---
title: "GFA - Data Visualization Exercise"
author: "Jake Rozran"
date: '2022-06-24'
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    fig.width = 9, 
    fig.height = 3.5, 
    fig.retina = 3,
    out.width = "100%",
    cache = FALSE,
    echo = FALSE,
    message = FALSE, 
    warning = FALSE,
    hiline = TRUE
)

library(tidyverse)
library(knitr)
library(kableExtra)

data("mpg")
# write.csv(mpg, "Data Visualization/Data Exercise/mpg.csv")
```

## Introduction

Let's take a look at the MPG dataset. This dataset contains a subset of the 
fuel economy data that the EPA makes available on http://fueleconomy.gov. It 
contains only models which had a new release every year between 1999 and 2008 - 
this was used as a proxy for the popularity of the car.

## Data

To access the data, please click the option that works for you below:

- [Microsoft Excel](https://drive.google.com/drive/u/1/folders/1JOr0jqhla5gZ2STOXuplNlV-a61DYCD8) (download the spreadsheet)
- [Google Sheets](https://docs.google.com/spreadsheets/d/10Gyloc1RvPy-URF6IH5hZZq0hiqexPyofAGmbRUuu2w/edit?usp=sharing) (copy the sheet to your own drive)

## Questions to Answer

1. Research: 
    - Explore the data to see what's in there
    - What is the range, median, and mean for displacement (`disp`), year, # of 
    engine cylinders (`cyl`), city mpg (`cty`), and highway mpg (`hwy`)?

```{r explore}
mpg %>% 
    head() %>%
    kbl() %>%
    kable_material(c("striped", "hover"))
```

2. Research:
    - Pick a car manufacturer
    - How many models does they have that have been around from 1999 - 2008?
    - Does one model have better or worse gas mileage than the others?

```{r research}
mnf <- "ford"
models <- length(unique(mpg$model[mpg$manufacturer == mnf]))

max_mods <- mpg %>% 
    filter(manufacturer == mnf) %>% 
    group_by(model) %>% 
    summarise(first_year = min(year),
              last_year = max(year), 
              mean_mpg_cty = mean(cty),
              mean_mpg_hwy = mean(hwy)) %>% 
    mutate(longest = last_year - first_year)
```

Example:
- Pick a car manufacturer: *`r mnf`*
- How many models does they have? *`r models`*
- Does one model have better or worse gas mileage than the others? *The mustang, *
*which is the only car here, has slightly better gas mileage than the *
*trucks/suvs.*

3. Plot:
- Bar Chart (2 variables):
    - Using the model that has been running the longest, make a bar chart that shows 
    both the `cty` and `hwy` mpg over time
    - Does that model have multiple `cyl` options? If so, plot those in separate 
    panels (aka facets)
    - Does that model [also] have multiple transmissions (`trans`), plot those 
    in separate panels (facets)

Example:

```{r bar_chart}
plot_dat <- mpg %>% 
    filter(manufacturer == mnf &
               model == "mustang") %>% 
    group_by(year, model) %>% 
    summarise(cty = mean(cty),
              hwy = mean(hwy)) %>% 
    pivot_longer(cols = c("cty", "hwy"), names_to = "mpg_type", values_to = "mpg")

ggplot(plot_dat, aes(x = factor(year), y = mpg, group = mpg_type, fill = mpg_type)) +
    geom_bar(stat = "identity", position = "dodge") + 
    scale_fill_manual(values = c("#1a3f6f", "#52c0ea")) + 
    ggtitle("Ford Mustang - City vs. Highway MPG",
            subtitle = "1999 vs. 2008") +
    xlab("Year") +
    ylab("Miles per Gallon (mpg)") +
    theme(panel.background = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.major.y = element_line(color = "light gray"),
          axis.ticks = element_blank(),
          legend.position = "none")
```

```{r bar_chart_facets}
plot_dat <- mpg %>% 
    filter(manufacturer == mnf &
               model == "mustang") %>% 
    group_by(year, model, cyl) %>% 
    summarise(cty = mean(cty),
              hwy = mean(hwy)) %>% 
    pivot_longer(cols = c("cty", "hwy"), names_to = "mpg_type", values_to = "mpg")

ggplot(plot_dat, aes(x = factor(year), y = mpg, group = mpg_type, fill = mpg_type)) +
    geom_bar(stat = "identity", position = "dodge") + 
    scale_fill_manual(values = c("#1a3f6f", "#52c0ea")) + 
    facet_wrap(~ cyl) +
    ggtitle("Ford Mustang - City vs. Highway MPG",
            subtitle = "1999 vs. 2008") +
    xlab("Year") +
    ylab("Miles per Gallon (mpg)") +
    theme(panel.background = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.major.y = element_line(color = "light gray"),
          axis.ticks = element_blank(),
          legend.position = "none",
          strip.background = element_blank())
```

```{r bar_chart_more_facets}
plot_dat <- mpg %>% 
    filter(manufacturer == mnf &
               model == "mustang") %>% 
    mutate(trans = ifelse(grepl("auto", trans), "automatic", "manual")) %>% 
    group_by(year, model, cyl, trans) %>% 
    summarise(cty = mean(cty),
              hwy = mean(hwy)) %>% 
    pivot_longer(cols = c("cty", "hwy"), names_to = "mpg_type", values_to = "mpg")

ggplot(plot_dat, aes(x = factor(year), y = mpg, group = mpg_type, fill = mpg_type)) +
    geom_bar(stat = "identity", position = "dodge") + 
    scale_fill_manual(values = c("#1a3f6f", "#52c0ea")) + 
    facet_wrap(cyl ~ trans) +
    ggtitle("Ford Mustang - City vs. Highway MPG",
            subtitle = "1999 vs. 2008") +
    xlab("Year") +
    ylab("Miles per Gallon (mpg)") +
    theme(panel.background = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.major.y = element_line(color = "light gray"),
          axis.ticks = element_blank(),
          legend.position = "none",
          strip.background = element_blank())
```

4. Review:
    - Does anything stick out in your bar charts?
    - If so, can you find an explanation for those things?