---
title: "Design Team Survey"
author: "Jake Rozran"
date: "2021-04-08"
output: html_document
---

```{r setup, include = FALSE, warnings = FALSE, message = FALSE}
source("R/get_data.R")
source("R/plot_data.R")
dat <- read_in_data("data/raw/Individual Design Preferences (Responses) - Form Responses 1.csv")
```

# Design Team Preferences

The design team, overall, prefers doing Design Strategy & Research and 
Interaction Design, followed closely with People Management. Less favored are 
Content Design and Visual Design.

This is not to say that these groups are universally liked or not liked. Within 
each area, there are specific preferences and dislikes. 

For example, within a less preferred area, Visual Design, the function of 
Product Design is highly preferred. On the flip side of this: Within the 
preferred area of Design Strategy & Research, Qualitative Research is a less 
preferred area.

## Overall Preferences

```{r overall, echo = FALSE, fig.width = 12, warnings = FALSE, message = FALSE}
plot_high_level(dat)
```

## Design Strategy & Research Preferences

```{r Design, echo = FALSE, fig.width = 12, warnings = FALSE, message = FALSE}
plot_design_data(dat)
```

* **Point** represents the average preference score
* The confidence interval is bounded on the **lower end** with the minimum 
preference score
* The confidence interval is bounded on the **upper end** with the maximum 
preference score

## Visual Design Preferences

```{r visual, echo = FALSE, fig.width = 12, warnings = FALSE, message = FALSE}
plot_visual_data(dat)
```

* **Point** represents the average preference score
* The confidence interval is bounded on the **lower end** with the minimum 
preference score
* The confidence interval is bounded on the **upper end** with the maximum 
preference score

## Interaction Design Preferences

```{r interaction, echo = FALSE, fig.width = 12, warnings = FALSE, message = FALSE}
plot_interaction_data(dat)
```

* **Point** represents the average preference score
* The confidence interval is bounded on the **lower end** with the minimum 
preference score
* The confidence interval is bounded on the **upper end** with the maximum 
preference score

## Content Design Preferences

```{r content, echo = FALSE, fig.width = 12, warnings = FALSE, message = FALSE}
plot_content_data(dat)
```

* **Point** represents the average preference score
* The confidence interval is bounded on the **lower end** with the minimum 
preference score
* The confidence interval is bounded on the **upper end** with the maximum 
preference score

## People Management Preferences

```{r people, echo = FALSE, fig.width = 12, warnings = FALSE, message = FALSE}
plot_people_data(dat)
```

* **Point** represents the average preference score
* The confidence interval is bounded on the **lower end** with the minimum 
preference score
* The confidence interval is bounded on the **upper end** with the maximum 
preference score

# Individual Preferences

```{r individual_preferences, echo = FALSE, fig.width = 12, fig.height = 9, warnings = FALSE, message = FALSE}
plot_individual_preferences(dat)
```

For each person, average score in each area was calculated and ranked. 5 is the 
highest rank for an individual and 1 is the lowest rank. 

# High Level Areas & People Who Prefer Them

For each high level design area, who has this ranked their highest?

```{r table_preferences, echo = FALSE, fig.width = 12, fig.height = 9, warnings = FALSE, message = FALSE}
library(knitr)

sumdat <- top_people_per_group(dat)

kable(sumdat)
```