---
title: "Analysis of DKAN Community"
author: "Jake Rozran"
date: "2021-04-06"
output: html_document
---

```{r setup, include = FALSE, warning = FALSE}
source("R/get_fork_data.R")

per_page <- 100

repo <- "getDKAN/dkan"
dkan_dat <- get_fork_data(repo, per_page)
dkan_dat <- clean_fork_data(dkan_dat, repo)

dkan_repo <- get_repo_data(repo)

repo <- "ckan/ckan"
ckan_dat <- get_fork_data(repo, per_page)
ckan_dat <- clean_fork_data(ckan_dat, repo)

ckan_repo <- get_repo_data(repo)
```

This is an analysis of the [getDKAN](https://github.com/GetDKAN)/[dkan](https://github.com/GetDKAN/dkan) 
and [ckan](https://github.com/ckan)/[ckan](https://github.com/ckan/ckan) repositories.

*This analysis was last run: `r Sys.time()`*

All of the data and code can be found in the [CivicActions](https://civicactions.com) 
[Data Science GitHub Repo](https://github.com/CivicActions/datascience/tree/main/ad-hoc%20analysis/DKAN_forks).

# How many times has dkan been forked?

dkan has been forked `r max(dkan_dat$fork_num)` times since 
`r format(min(dkan_dat$created_at, na.rm = TRUE), "%B %d, %Y")`.

```{r forks_over_time_dkan, echo = FALSE, warning = FALSE}
source("R/analysis_functions.R")
plot_forks_over_time(dkan_dat)
```

# How many times has ckan been forked?

ckan has been forked `r max(ckan_dat$fork_num)` times since 
`r format(min(ckan_dat$created_at, na.rm = TRUE), "%B %d, %Y")`.

*Note: Branches were removed from this plot - there were too many to show clearly.*

```{r forks_over_time_ckan, echo = FALSE, warning = FALSE}
source("R/analysis_functions.R")
plot_ckan_forks_over_time(ckan_dat)
```

# Are there active forks of dkan?

Here are the forks that have pushes to them at least 30 days after the initial fork. 

```{r active_repos_dkan, echo = FALSE, warning = FALSE}
active_dat <- rbind(dkan_repo, dkan_dat[dkan_dat$activity > 30, 
                                        c("full_name", "created_at", "pushed_at")])

plot_active_forks(active_dat)
```

# Are there active forks of ckan?

Here are the forks that have pushes to them at least 30 days after the initial fork. 

```{r active_repos_ckan, echo = FALSE, fig.height = 40, warning = FALSE}
active_dat <- rbind(ckan_repo, ckan_dat[ckan_dat$activity > 30, 
                                        c("full_name", "created_at", "pushed_at")])

plot_active_forks(active_dat)
```

# dkan vs. ckan

Comparing the dkan open source community compared to that of ckan. 

```{r dkan_ckan, echo = FALSE, warning = FALSE}
plot_ckan_dkan_forks_over_time(dkan_dat, ckan_dat)
```